\documentclass[12pt]{article}
  
\textwidth       165mm
\oddsidemargin     0in
%  \advance\oddsidemargin by -1in
\evensidemargin    0in
%  \advance\evensidemargin by -1in
\textheight        9.75in
\topmargin         0in
  \advance\topmargin by 0in %-0.5in
\headheight        0pt
\headsep           0pt
\topskip           0pt
 
%\pagestyle{empty}
\begin{document}

%\vspace*{1ex}
\begin{center}
   \Large {\bf{ADRIAN A. DRAGULESCU}}
\end{center}

\noindent
\makebox[165mm]{Email: adrian.dragulescu@constellation.com 
        \hfill 9439 Lovat Rd.}\\
\makebox[165mm]{Phone: 410-468-3778 \hfill Fulton, MD 20759}
\noindent
\rule{165mm}{1mm}

\vspace*{2pt}
\noindent
\large\textsf{\textbf {Experience}}

\vspace*{-8pt}
\noindent
\rule{165mm}{0.5mm}
\normalfont\normalsize

\noindent
{\bf (2002-2005) Risk Management Group, Constellation Commodities Group.} 
\begin{list}{$\bullet$}
   {\setlength{\itemsep}{0ex}
    \setlength{\parsep}{1ex}}
    \item Involved in many aspects of quantitative risk management.
    These include validation of models (physical and financial)
    developed by front-office quants, development of independent
    models, and benchmarking of in-house models using third party
    models.

    \item Physical models experience include: temperature model, load
    forecasting model, spot price simulation, fundamental asset
    valuation, estimation of congestion risk (FTR's and TCC's),
    fundamental gas model, gas transportation model, plant outage
    model, GMAR model.

    \item Financial models experience include: option valuation,
    modeling of customer attrition in load serving deals, asset
    valuation with spread options, risk neutral forward curve
    simulations, VaR methodology, RAROC, etc.

    \item Involved in the deal review process.  Contributed to
    identification of risks in new deals.  Built a temperature and
    load forecast model for independent valuation of deals.    

    \item Developed a tool used by the Credit Group to calculate the
    maximum potential exposure.  The tool also calculates the margin
    requirements and the cost of credit by deal and counterparty.

    \item Performed periodical regional analysis on historical forward
    curves to propose relevant stress tests for entire portfolio.
    Extensive experience with valuation and risks of weather options.
\end{list}

\noindent
\rule{165mm}{0.3mm}
{\bf (2001-2002) Econometric Support Group, International Monetary Fund.}
\begin{list}{$\bullet$}
   {\setlength{\itemsep}{0ex}
    \setlength{\parsep}{1ex}}
    \item Provided mathematical and computer support to IMF
    economists.  Taught a Matlab course to IMF economists.  Learned
    and applied novel econometric techniques.

    \item Used various statistical software.  Matlab, Mathematica,
    Splus/R, Gauss, Eviews.
\end{list}

\noindent
\rule{165mm}{0.3mm}
{\bf (1996-2002) PhD student in Physics, University of Maryland,
  College Park.}
\begin{list}{$\bullet$}
   {\setlength{\itemsep}{0ex}
    \setlength{\parsep}{1ex}}
    \item Derived new analytical formula for the probability distribution 
	of returns for a geometrical Brownian motion with stochastic 
	volatility. Tested the model with Dow-Jones data and found 
	excellent agreement. Applications range from option pricing to 
	risk management. 

    \item Attended PhD courses in Finance. Assignments on CAPM theory, 
	portfolio immunization, yield curve fitting, pricing of bonds 
	and derivatives, lattice models and dynamic programming. 
	Implemented Monte Carlo	valuation of options using Matlab. 

    \item Analyzed large amounts of data from the IRS and US Census to
	study the distribution of incomes in the US. Used Perl to
	filter the data, and Matlab to process and visualize the
	data. Performed parameter estimations, linear and non-linear
	regressions.

\end{list}

\large\textsf{\textbf {Computer skills}}

\vspace*{-8pt}
\noindent
\rule{165mm}{0.5mm}
\normalfont\normalsize
\vspace*{-12pt}
\begin{list}{$\bullet$}
   {\setlength{\itemsep}{0ex}
    \setlength{\parsep}{1ex}} 
    \item Matlab, R/SPlus, C, C++, Perl, SQL, Excel/VBA, Mathematica,
        Fortran.  Excellent knowledge of Latex.  Worked under AIX,
        Linux, Solaris, and Windows operating systems.
\end{list}



\large\textsf{\textbf {Publications}}

\vspace*{-8pt}
\noindent
\rule{165mm}{0.5mm}
\normalfont\normalsize
\vspace*{-12pt}
\begin{list}{$\bullet$}
   {\setlength{\itemsep}{0ex}
    \setlength{\parsep}{1ex}} 
  \item Ramamurtie, S., Sogomnonian, A., Dragulescu, A., and Li, L.,
  {\it Derivative Modeling Approaches in Real Asset Valuation}, in Real
  Options and Energy Management, 217-237 (2002). 

  \item Dragulescu, A.\ and Yakovenko, V.M.\, {\it Modeling of Complex
  Systems: Seventh Granada Lectures}, AIP Conference Proceedings {\bf 661},
  New York, 180-183 (2003).

  \item Dragulescu, A.\ and Yakovenko, V.M.\, Probability distribution
  of returns for a model with stochastic volatility, {\it Quantitative
  Finance}, {\bf 2}, 443-453 (2002).

  \item Dragulescu, A.\ and Yakovenko, V.M.\, Exponential and power-law
  probability distributions of wealth and income in the United Kingdom
  and the United States, {\it Physica A} {\bf 299}, 213-221 (2001).

  \item Dragulescu, A.\ and Yakovenko, V.M.\, Evidence for the
  exponential distribution of income in the USA, {\it European
  Physical Journal B} {\bf 20}, 585-589 (2001).

  \item Dragulescu, A.\ and Yakovenko, V.M.\, Statistical mechanics of
  Money, {\it European Physical Journal B} {\bf 17}, 723-729 (2000).

  \item Dragulescu, A.\ and Yakovenko, V.M.\, {\it Theory of angular
  magnetoresistance oscillations in Tl$_2$Ba$_2$CuO$_6$}, Physical
  Review B {\bf 60} 6312-6315, (1999).
\end{list}


\end{document}


%% \vspace*{0pt}
%% \noindent
%% \large\textsf{\textbf {Education, Training, and Work Experience}}

%% \vspace*{-8pt}
%% \noindent
%% \rule{165mm}{0.5mm}
%% \normalfont\normalsize

%% \vspace*{-12pt}
%% \begin{list}{$\bullet$}
%%    {\setlength{\itemsep}{0ex}
%%     \setlength{\parsep}{1ex}} 
%%     \item (2001-2002) Econometric Support Group, International Monetary Fund.
%%     \item (1996-2002) PhD student in Physics, University of Maryland, 
%%           College Park, \mbox{GPA: 3.91}
%%     \item (1991-1996) MS in Physics, West University of Timisoara, 
%%           Romania, GPA: 3.98
%% \end{list}


%% \item Invited talk on Econophysics at FirmWide Risk division of
%%   Goldman, Sachs and Co., 03/2001.

%% \item Presentation at 3rd Econophysics conference, Applications of
%%   Physics in Financial Analysis, London, 12/2001.

%% \item Seminar at Department of Statistics, University of Maryland, 04/2002.

%% \item Seminar at Institute of Physical Sciences and Technology,
%%   Maryland, 05/2002.

%% \item First prize at GRID, campus wide research competition, 04/2001.


